Hope

### 2024-05-29 paper/IEEES/paper.tex
Added Coq introduction and soundess of schnor

\noindent 
Finally, voters or scrutineers inspect these proofs and accept or reject the election results based on 
the verification of these proofs. In practice, this means that during the execution of an election, 
electronic voting software generates data, and voters and scrutineers verify the conformity of 
this data using independently written computer programs. The rationale is that if there is 
any discrepancy in the electronic voting system, at least one scrutineer or voter would detect it.
It is important to note that end-to-end verifiability is a valuable feature because it 
allows for the verification of the election results by checking the proofs of correctness 
only after the election has concluded. This ensures that the election process was conducted 
properly and that the results are accurate, but it is applied after the voting has taken place.
The question arises: can we use it before an election?
The answer is yes; we use a formal language to express end-to-end verifiability, or parts of 
it and develop various components of electronic voting 
software in this formal language. This process is called as formal verification and it ensures 
that the software always produces valid proofs, 
which are consistently accepted by voters and scrutineers. In other words, formal verification
can be employed to develop reliable electronic voting software.
In fact, formal verification has emerged as a promising solution 
to eliminate potential bugs from software, and in recent years it has been increasingly 
adopted in real-world software applications \cite{10.1145/1111037.1111042}, 
including cryptography \cite{8835346,10.1145/3133956.3134043,190894,10.1145/2701415,
10.1145/2660267.2660370,10.1145/3319535.3363211}.

In this paper, we present a certified implementation of the Sigma protocol --an efficient 
type of zero-knowledge proof-- and its Parallel, And, Eq, Or, and Neq compositions in 
the formal language of Coq proof assistant. Given that the formal language of Coq 
is constructive, we get an implementation that can be executed on a computer.

We have formalised and analysed the interactive version of 
the Sigma protocol, but in practice it is not convenient due to the required interaction. 
Therefore, all Sigma protocol implementations use the Fiat-Shamir 
transformation \cite{10.5555/36664.36676} to make them non-interactive. This involves 
using a hash function to replace the randomness of the public-coin verifier, though 
some care is required \cite{10.1007/978-3-642-34961-4_38}.
To make our formalisation self-contained and independent of external libraries, we have 
encoded SHA-256 in Coq and proven its usual correctness properties. Additionally, we 
have implemented efficient prime field arithmetic procedures and the Schnorr group to 
ensure our library is concrete and executable. Finally, we extract WebAssembly and 
Rust code from our certified implementation, one of the novelties of our 
formalisation.

There are numerous implementations of sigma protocol in various languages, 
e.g., Helios is written in Python, Belenois is written in OCaml, and SwissPost is written in Java.
However, there are two main issues with these implementations: 
(i) the same code is written twice 
once for the front-end (JavaScript, TypeScript) and once for the back-end (Python, OCaml, or Java) and 
(ii) none of these implementations offer any formal guarantees about the correctness of the code.
Therefore, we use our formalisation to model the sigma protocol implemented in Helios, 
Belenois, and SwissPost voting systems to demonstrate the usablity of 
our library. Unlike Helios and SwissPost,
we write one implementation and extract WebAssembly (front-end) and Rust (back-end). 
Belenois is slightly different in this respect and uses Js\_of\_ocaml 
to compile the OCaml code into JavaScript so it has only one 
implementation written in OCaml; nonetheless it is not verified 
and offers no formal guarantees. To the best of our knowledge, 
this is the firstformal verification of sigma protocol that can be used at 
the front-end (WebAssembly code) and back-end (Rust code).

\subsection{Outline}

\section{Sigma Protocol}
Despite the recent growth and popularity of zero-knowledge succinct 
argument of knowledge (ZKSNARK), sigma protocol remains a
leading cryptographic proof system in privacy-preserving voting systems. 
Sigma protocol is used in Helios --a widely popular voting system-- \cite{adida2008helios}, 
Belenois --used in French elections for overseas 
voters\footnote{VVFE, used in French elections, is a derivative of (part of) Belenios and 
inherited all the zero-knowledge proofs from Belenois.}-- \cite{cortier2023french}, and 
SwissPost --used in Swiss elections for overseas voters-- voting 
systems \cite{10.1007/978-3-031-15911-4_4} (\textbf{Look for more examples}). 
Moreover, recently zero-knowledge proof community started a movement to standardise
the sigma protocol \cite{ZKProof}.
One of the main reasons for its popularity in privacy-preserving voting systems is its
well-understood security.  Other application of sigma protocol 
include identification schemes, (cite more work).

@@

\section{Coq formalisation}

  We briefly explain the Schnorr protocol, which is very similar to figure \textbf{refer here to sigma protocol picture}.
  Given some public input $(G, g, q, h)$ where $G$
  is a cyclic group of prime order $q$, $g$ and $h$ are two 
  generators of the group $G$, the prover claims that they know a
  witness $w$ for the statement $h = g^w$; the existence of such
  a $w$ is immediate because $g$ generates the group. However,
  does the prover know the witness $w$? In order to convince the
  verifier, the prover and the verifier do the following:
  \begin{itemize}
    \item the prover picks a random number $u$, computes $c = g^u$,
    and sends $c$ to the verifier.
    \item the verifier picks a random challenge $e$ and sends it to
    the prover
    \item the prover computes $t = u + e * w$ and sends $t$ to the
    verifier
  \end{itemize}

The verifier accepts if $g^t = c * h^e$, otherwise rejects. We can prove that 
this protocol has completeness, special soundness, and special honest-verifier 
zero-knowledge proof.

\begin{itemize}
  \item completeness: when $P$ and $V$ both follows the protocol, $V$ accepts the proof, i.e., 
  the verification equation checks. We can see by algebraic simplification that is the case.
    \begin{align*}
      g^t = g^{u + e * w} = g^u * (g^w)^e = c * h^e
    \end{align*}
  \item special soundness:

@@

\begin{lstlisting}[language=Coq]
(*Real transcript (involves secret x)*)
Definition schnorr_protocol (x : F) (g : G) (u c : F) : 
 sigma_proto :=  ([g^u]; [c]; [u + c * x]).

@@

We prove the completeness and special soundness property of the Schnorr protocol, 
as shown in the figure .... We however cannot prove the special honest-verifier 
zero-knowledge property yet because it requires reasoning about probability that 
we discuss in the next section.

\begin{lstlisting}[language=Coq]
Lemma schnorr_completeness : 
forall (r c : F) (a : t G 1) (c r : t F 1),
(a; c; r) = (schnorr_protocol x g r c) ->
accepting_conversation g h (a; c; r) = true.
Proof. (* proof terms omitted *) Qed.

@@

Lemma special_soundness: 
forall (a : G) (ca ra cb rb : F), ca <> cb ->
accepting_conversation g h ([a]; [ca]; [ra]) = true ->  
accepting_conversation g h ([a]; [cb]; [rb]) = true ->
exists y : F, g^y = h /\ y = ((ra - rb) * inv (ca - cb)).
Proof using -(x R). (* proof terms omitted *) Qed.

@@

  \begin{lstlisting}[language=Coq]

@@

\begin{lstlisting}[language=Coq]
(* Probability Monad *)
Definition Ret {A : Type} (x : A) : 
  dist A := [(x, one)].

@@

\begin{lstlisting}[language=Coq]
(* Distribution that involves the secret x *)
Definition schnorr_distribution  (lf : list F) 
  (Hlfn : lf <> List.nil) (x : F) (g : G) (c : F) : 
  dist sigma_proto :=
  (* draw u from a random distribution *)
  u <- (uniform_with_replacement lf Hlfn) ;;
  Ret (schnorr_protocol x g u c).

@@

\begin{lstlisting}[language=Coq]
Fixpoint repeat_dist_ntimes_vector {A : Type} 
(d : dist A) (n : nat) : dist (Vector.t A n) := 
match n with 
| 0 => Ret (@Vector.nil A)
| S n' => 
  Bind d (fun u => 
    Bind (repeat_dist_ntimes_vector d n')
    (fun v => Ret (Vector.cons _ u _ v)))
end.

@@

\subsection{Efficient Modular Arithmetic}
 As we stated that our formalisation is  
 abstract and can be instantiated with 
 a suitable group and field. In order 
 to run our code, we have developed 
 a formally verified Schnorr group (\textbf{cite here}). 
\begin{lstlisting}[language=Coq]
Section SchnorrGroup. 
  Context 
    {k p q : Z}
    {Hk : p = k * q + 1}
    {Hp : prime p}
    {Hq : prime q}.

@@

\section{MetaCoq}
  Bas Spitters

\section{Web Assembly and Rust from the Coq Formalisation}
  Bas Spitter

@@

\section{Related Work}
  There are three work. Giles Barthe does not extract to executable code, 
  CryptoHol uses law of excluded middle, and thomas haines work is more about 
  verifying a transcript rather than constructing it. Moreover, 
  it does not reason about probabilities in intuitive way.

@@

\section{Conclusion, Future Work, and Limitations}
  In this paper, we present a certified implementation 
  that can be readily used by voting community and 
  we demonstrated the usefulness by encoding Helios, 
  Belenois, and SwissPost using our primitives. 
  Moreover, our formalisation extracts to WebAssembly and 
  Rust without duplicate efforts.

>>>>

\noindent 
Finally, voters or scrutineers inspect these proofs and accept or reject the election results based on 
the verification of these proofs. In practice, this means that during the execution of an election, 
electronic voting software generates data, and voters and scrutineers verify the conformity of 
this data using independently written computer programs. The rationale is that if there is 
any discrepancy in the electronic voting system, at least one scrutineer or voter would detect it.
It is important to note that end-to-end verifiability is a valuable feature because it 
allows for the verification of the election results by checking the proofs of correctness 
once the election has concluded. This ensures that the election process was conducted 
properly and that the results are accurate, but it is applied during or after the voting has taken place.
However, can we use it before an election?
The answer is yes; we use a formal language to express end-to-end verifiability, or parts of 
it, and develop various components of electronic voting 
software in this formal language. This process is called as  formal verification, or correct-by-construction,
and it ensures that the software always produces valid proofs, 
which are consistently accepted by voters and scrutineers. In other words, formal verification
can be employed to develop reliable electronic voting software.
In fact, formal verification has emerged as a promising solution 
to eliminate potential bugs from software, and in recent years it has been increasingly 
adopted in real-world software applications \cite{10.1145/1111037.1111042}, 
including cryptography \cite{8835346,10.1145/3133956.3134043,190894,10.1145/2701415,
10.1145/2660267.2660370,10.1145/3319535.3363211}.

In this paper, we present a certified implementation of sigma protocol --an efficient 
type of zero-knowledge proof-- and its Parallel, And, Eq, Or, and Neq compositions in 
the formal language of Coq proof assistant. 
We have formalised and analysed the interactive version of 
the Sigma protocol, but in practice it is not convenient due to the required interaction. 
Therefore, all Sigma protocol implementations use the Fiat-Shamir 
transformation \cite{10.5555/36664.36676} to make them non-interactive. This involves 
using a hash function to replace the randomness of the public-coin verifier, though 
some care is required \cite{10.1007/978-3-642-34961-4_38}.
To make our formalisation self-contained and independent of external libraries, we have 
encoded SHA-256 in Coq and proven its usual correctness properties. Additionally, we 
have implemented efficient prime field arithmetic procedures and the Schnorr group to 
ensure our library is concrete and executable. Finally, we extract WebAssembly and 
Rust code from our certified implementation, one of the novelties of our 
formalisation.

There are numerous implementations of sigma protocol in various languages, 
e.g., Helios is written in Python, Belenois is written in OCaml, and SwissPost is written in Java.
However, there are two main issues with these implementations: 
(i) the same code is written twice 
once for the front-end (JavaScript, TypeScript) and once for the back-end (Python, OCaml, or Java) and 
(ii) none of these implementations offer any formal guarantees about the correctness of the code.
Therefore, we use our formalisation to model the sigma protocol implemented in Helios, 
Belenois, and SwissPost voting systems to demonstrate the usablity of 
our library. Unlike Helios and SwissPost,
we write one implementation and extract WebAssembly (front-end) and Rust (back-end) (\textbf{using the MetaCoq library}).
Belenois is slightly different in this respect and uses Js\_of\_ocaml 
to compile the OCaml code into JavaScript so it has only one 
implementation written in OCaml; nonetheless it is not verified 
and offers no formal guarantees. To the best of our knowledge, 
this is the firstformal verification of sigma protocol that can be used at 
the front-end (WebAssembly code) and back-end (Rust code).

\subsection{Outline}
The rest of the paper is organised as follows: in section \ref{sigma_protocol}
we explain sigma protocol and its security properties.

\section{Sigma Protocol}\label{sigma_protocol}
Despite the recent growth and popularity of zero-knowledge succinct 
argument of knowledge (ZKSNARK), sigma protocol remains a
leading cryptographic proof system in privacy-preserving voting systems. 
Sigma protocol is used in Helios --a widely popular voting system-- \cite{adida2008helios}, 
Belenois --used in French elections for overseas 
voters\footnote{VVFE, used in French elections, is a derivative of (part of) Belenios and 
inherited all the zero-knowledge proofs from Belenois.}-- \cite{cortier2023french}, and 
SwissPost --used in Swiss elections for overseas voters-- voting 
systems \cite{10.1007/978-3-031-15911-4_4} (\textbf{Look for more examples}). 
Moreover, recently zero-knowledge proof community started a movement to standardise
the sigma protocol \cite{ZKProof}.
One of the main reasons for its popularity in privacy-preserving voting systems is its
well-understood security.  Other application of sigma protocol 
include identification schemes, (cite more work).

@@

\section{The Coq Theorem Prover}
\textbf{FIXME:this seems too much of tutorial Coq so let me know your thoughts. We 
can explain MetaCoq here as well and the extraction to Rust and WebAssembly
so that it justifies this tutorial}
The Coq theorem prover \cite{the_coq_development_team} is a computer program that interacts with users, 
enabling them to encode mathematical definitions, express specifications (true statements) about 
these definitions, and formally prove that the definitions imply the specifications. 
A user first defines their mathematical object (definition) and then figure 
out some  true statements (specifications) about 
that object. Once the user has definition 
and specifications, they need to prove 
that the definition satisfies the specifications 
(proof writing). In general, amongst these three steps, 
the proof writing step is the most challenging and important step. 
During the proof writing, the user interacts with the Coq theorem prover 
via \emph{tactics}, a domain specific language 
to ease the proof writing. Even though the Coq theorem 
provides some amount of automation and proof 
search, most of the time it requires human assistance to finish the proof. 
It is one the most popular and robust theorem, and
one of reasons for its popularity is 
dependent types, that makes it possible to encode
any mathematical statement in its logic.
It has been used to verify many real world software projects and mathematical 
artefacts. For example, Coq has been used to 
formally verify CompCert \cite{10.1145/1111037.1111042}, 
a C compiler used by many companies\footnote{https://www.absint.com/partners.htm}, 
Fiat-Crypto \cite{8835346} 
used in BoringSSL --a cryptographic library used in Chrome, Android, 
and CloudFlare--, ConCert \cite{10.1145/3372885.3373829}, 
a smart contract certification framework, etc. \textbf{FIXME: More examples}

\subsubsection*{Definitions, Specifications, and Proofs}
In this section, we demonstrate how to encode definitions, write specifications,
and formally prove that definitions satisfy the specifications 
in the Coq theorem prover by an example of 
natural numbers (natural numbers is the set $\{0, 1, 2, 3, \dots \}$). 
The set of natural numbers $Nat$ is the set of elements defined by the 
following clauses:
\begin{itemize}
  \item \emph{Zero}, represents $0$, is in the set Nat ($Zero \in Nat$)
  \item if $n$ is in the set Nat, then \emph{Succ n}, represents $n + 1$, 
    is also in the set Nat (if $n \in Nat$, then $Succ \text{ }n \in Nat$)
\end{itemize}

\noindent 
This representation of natural numbers is called 
inductively defined set where the base case, or starting point,
is Zero (constant symbol), and if we have a natural number $n$, then we can 
get the next natural number by prefixing Succ (unary function symbol) to $n$.  
Using this encoding of natural numbers, we can represent 
$1$ by \emph{Succ Zero}, and $2$ by \emph{Succ (Succ Zero)}, 
and so on. We encode the set \emph{Nat} in Coq as inductively defined data type, 
shown in Listing \ref{ind_nat}, with 
two constructors: \emph{Zero} and \emph{Succ}. 
\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
Inductive Nat : Type := 
| Zero : Nat 
| Succ : Nat -> Nat.
\end{lstlisting}

With the definition of natural numbers at our disposal,
we can define addition, subtraction, multiplication, division, and 
many other mathematical functions on natural numbers in the Coq theorem prover. 
However, we only define the addition function,
shown in Listing \ref{add_fn}, to demonstrate the concept. 
In Coq, \emph{Fixpoint} is a keyword 
for defining function, followed by the name of the function (\emph{plus}), 
arguments (\emph{m} and \emph{n}), and the body (definition) of the function.
The body of plus shown in Listing \ref{add_fn} is Coq encoding of the 
following two clauses:
\begin{enumerate}
  \item plus Zero n = n 
  \item plus (Succ m) n = Succ (plus m n)
\end{enumerate}

\noindent 
The first clause amounts to $0 + n = n$ and the second clause
amounts to $ (1 + m) + n = 1 + (m + n)$.

\begin{lstlisting}[frame=single, language=Coq, caption={Addition of two Natural Numbers},
  label={add_fn},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
Fixpoint plus (m n : Nat) :=
  match m with
  | Zero => n
  | Succ m' => Succ (plus m' n)
  end.

So far we have just definitions of natural numbers and addition on them.
Now, it is time to define some specification (true statement) about
the addition operation, on natural numbers. From mathematical 
literature, we know that the addition operation on natural
numbers is associative and commutative. For simplicity, we
prove that our definition of addition on natural numbers is commutative, shown in 
Listing \ref{plus_comm}, and it is precisely the \emph{specification} for 
our addition operation.

\begin{lstlisting}[frame=single, language=Coq, caption={Addition is Commutative},
  label={plus_comm},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
Theorem plus_commutative : 
  forall n m, plus n m = plus m n. 
Proof.
  induction n.
  (* base case *)
  + intros m.
  (* proof terms omitted *)
  (* inductive case *)  
  + intros m.
    rewrite IHn.
    (* proof terms omitted *)
Qed.

In Coq, \emph{Theorem} is the keyword
to define a specification, followed by the name (\emph{plus\_comm}). 
It says that for any two arbitrary natural numbers $m$ and $n$, 
encoded as \texttt{forall n m}, adding $n$ and $m$ is the same
as adding $m$ and $n$, encoded as \texttt{plus n m = plus m n}.
To write a formal proof of this statement, we tell the Coq theorem 
prover that we want to use the tactic language by 
stating the keyword \emph{Proof}. After finishing the proof, 
we use the keyword \emph{Qed} to inform Coq that our proof is 
finished. The moment Coq sees \emph{Qed},
it ensures that the proof is complete and correct according to its 
underlying logic. If we try to use Qed without finishing the proof,
Coq will not let us do so. Therefore, once we have Qed for any 
specification, by just trusting the Coq theorem prover we can be 
sure that our proof is correct. However, at this point, 
the curious reader can argue that why should we trust 
Coq because it is a computer program, similar any other 
computer program? Trusting Coq hinges on two things: 
(i) the meta theory, \emph{Calculus of Inductive Construction},
of Coq \cite{thierry1988calculus}
and (ii) its OCaml implementation \cite{the_coq_development_team}.
The meta theory of Coq has been scrutinised for decades
by many mathematicians and so far it has withstood all 
the scrutiny. The OCaml implementation of Coq  has a very 
small kernel and has been inspected by many computer scientists. 
In addition, there is a recent effort to develop more 
rigorous implementation for Coq proof checking \cite{10.1145/3371076} \textbf{FIXME: this is the place 
to state that we are following this path of MetaCoq}.

The keywords \emph{induction, intros, rewrite}
are tactics that are used to prove the statement that addition 
on natural numbers is commutative. 
The proof written between 
the keywords \emph{Proof} and \emph{Qed} amounts to the following: 
\begin{itemize}
  \item Base case: when $n$ is Zero, we need to prove that \texttt{plus Zero m = plus m Zero}
  \item Inductive case: when $n$ is Succ, we assume \texttt{plus m n = plus n m} 
      and we need to prove \texttt{plus (Succ m) n = plus n (Succ m)}
\end{itemize}  
\noindent
It is called proof by induction, and 
tactics are used to make the complicated 
process of proof writing easy.

\subsection{Schnorr Protocol Coq Encoding}

  We briefly explain the Schnorr protocol, which is very similar to figure \textbf{refer here to sigma protocol picture}.
  Given some public input $(G, g, q, h)$ where $G$
  is a cyclic group of prime order $q$, $g$ and $h$ are two 
  generators of the group $G$, the prover claims that they know a
  witness $w$ for the statement $h = g^w$; the existence of such
  a $w$ is immediate because $g$ generates the group. However,
  does the prover know the witness $w$? In order to convince the
  verifier, the prover and the verifier do the following:
  \begin{itemize}
    \item the prover picks a random number $u$, computes $a = g^u$,
    and sends $a$ to the verifier.
    \item the verifier picks a random challenge $c$ and sends it to
    the prover
    \item the prover computes $r = u + c * w$ and sends $r$ to the
    verifier
  \end{itemize}

The verifier accepts the transcript $(a, c, r)$ if $g^r = a * h^c$, otherwise rejects. We can prove that 
this protocol has completeness, special soundness, and special honest-verifier 
zero-knowledge proof.

\begin{itemize}
  \item completeness: when $P$ and $V$ both follows the protocol, $V$ accepts the proof, i.e., 
  the verification equation checks out. We can see by algebraic simplification that it is the case.
    \begin{align*}
      g^r = g^{u + c * w} = g^u * (g^w)^c = a * h^c
    \end{align*}
  \item special soundness: from two accepting 
  conversations $(a, c, r)$ and $(a, c', r')$ where $c \neq c'$,
  a polynomial-time extractor can extract a witness $w$, 
  which is equal to $(r - r') * (c - c')^{-1}$, 
  such that $g^w = h$. By means of algebraic simplification, 
  we can see that it is the case.  
  \begin{align}
    g^r = a * h^c = g^u * (g^w)^c = g^{u + w * c}  \\
    g^{r'} = a * h^{c'} = g^u * (g^w)^{c'} = g^{u + w * c'}
  \end{align}
  Diving the expression (1) with (2), we get
  \begin{align*}
    g^{(r-r')} = g^{w * (c - c')}
  \end{align*}
  and multiplying both sides by $(c - c')^{-1}$ we 
  get 
  \begin{align*}
    g^{(r-r') * (c - c')^{-1}} = g^{w}
  \end{align*}

@@

\begin{lstlisting}[frame=single, language=Coq, caption={Schnorr protocol},
  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
(*Real transcript (involves secret x)*)
Definition schnorr_protocol (x : F) (g : G) 
 (u c : F) : sigma_proto :=  
 ([g^u]; [c]; [u + c * x]).

@@

We prove the completeness and special soundness property of the Schnorr protocol, 
as shown in Lisitng \cite{comp_sound}. We however cannot prove the special honest-verifier 
zero-knowledge property yet because it requires reasoning about probability that 
we discuss in the next section.

\begin{lstlisting}[frame=single, language=Coq, caption={Completeness and Soundness},
  label={comp_sound},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
Lemma schnorr_completeness : 
forall (r c : F) (a : t G 1) (c r : t F 1),
(a; c; r) = (schnorr_protocol x g r c) ->
accepting_conversation g h (a; c; r) = true.
Proof. (* proof terms omitted *) Qed.

@@

Lemma special_soundness: 
forall (a : G) (ca ra cb rb : F), ca <> cb ->
accepting_conversation g h ([a]; [ca]; [ra]) ->  
accepting_conversation g h ([a]; [cb]; [rb]) ->
exists y : F, g^y = h /\ y = ((ra - rb) * inv (ca - cb)).
Proof using -(x R). (* proof terms omitted *) Qed.

@@

\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
    label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
    abovecaptionskip=-\medskipamount]

@@

\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
(* Probability Monad *)
Definition Ret {A : Type} (x : A) : 
  dist A := [(x, one)].

@@

\begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
(* Distribution that involves the secret x *)
Definition schnorr_distribution  (lf : list F) 
  (Hlfn : lf <> List.nil) (x : F) (g : G) (c : F) : 
  dist sigma_proto :=
  (* draw u from a random distribution *)
  u <- (uniform_with_replacement lf Hlfn) ;;
  Ret (schnorr_protocol x g u c).

@@

  \begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
    label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
    abovecaptionskip=-\medskipamount]
Fixpoint repeat_dist_ntimes_vector {A : Type} 
(d : dist A) (n : nat) : dist (Vector.t A n) := 
match n with 
| 0 => Ret (@Vector.nil A)
| S n' => 
  Bind d (fun u => 
    Bind (repeat_dist_ntimes_vector d n')
    (fun v => Ret (Vector.cons _ u _ v)))
end.

@@

\subsection{Efficient Modular Arithmetic}
 As we stated that our formalisation is  
 abstract and can be instantiated with 
 a suitable group and field. In order 
 to run our code, we have developed 
 a formally verified Schnorr group (\textbf{cite here}). 
 \begin{lstlisting}[frame=single, language=Coq, caption={Definition of Natural Number},
  label={ind_nat},captionpos=t, basicstyle=\ttfamily\footnotesize,
  abovecaptionskip=-\medskipamount]
Section SchnorrGroup. 
  Context 
    {k p q : Z}
    {Hk : p = k * q + 1}
    {Hp : prime p}
    {Hq : prime q}.

@@

\section{Web Assembly and Rust from the Coq Formalisation (MetaCoq)}
  Bas Spitter

@@

\section{Related Work, Future Work, and Limitations}
  There are three work. Giles Barthe does not extract to executable code, 
  CryptoHol uses law of excluded middle, and thomas haines work is more about 
  verifying a transcript rather than constructing it. Moreover, 
  it does not reason about probabilities in intuitive way.

@@

  In this paper, we present a certified implementation 
  that can be readily used by voting community and 
  we demonstrated the usefulness by encoding Helios, 
  Belenois, and SwissPost using our primitives. 
  Moreover, our formalisation extracts to WebAssembly and 
  Rust without duplicate efforts.
